Dependent Object Types

### 2012-09-22 doc/fool/article.tex
remove undef refs and conc

Let's first ignore the extension of the calculus requiring explicit
widenings introduced in~\ref{widening}. Then, we need to add one
intuitive rule to the subtyping judgment: $\textsc{$\sub$-path}$. If
$p$ (path-)reduces to $q$, and $T \sub q.L$, then $T \sub p.L$. Path
reduction is a simplified form of reduction involving only
paths. However, this means that the subtyping judgment, and
indirectly, all the typing-related judgments, now need to carry the
store in addition to the context so that path reductions can be
calculated.

@@

First, path reduction is not isomorphic to reduction anymore, since we
want to actually skip over widenings, as motivated by the last example
in~\ref{widening}.

@@

Proving the DOT calculus type-safe has been an interesting
adventure. We have shown that DOT does not satisfy preservation (also
known as subject-reduction), because a well-typed term can step to an
intermediate term that is not well-typed. We're open to ideas on how
to resolve this. In any case, the standard theorems of preservation
and progress are just one way to prove type safety, which simply
states that a well-typed term cannot be stuck. We are developing a
proof of type safety using logical relations.

>>>>

Let's first ignore the extension of the calculus requiring explicit
widenings. Then, we need to add one
intuitive rule to the subtyping judgment: $\textsc{$\sub$-path}$. If
$p$ (path-)reduces to $q$, and $T \sub q.L$, then $T \sub p.L$. Path
reduction is a simplified form of reduction involving only
paths. However, this means that the subtyping judgment, and
indirectly, all the typing-related judgments, now need to carry the
store in addition to the context so that path reductions can be
calculated.

@@

First, path reduction is not isomorphic to reduction anymore, since we
want to actually skip over widenings, as motivated by the example above.

@@

Proving the DOT calculus type-safe has been an interesting
adventure. We have shown that DOT does not satisfy preservation (also
known as subject-reduction), because a well-typed term can step to an
intermediate term that is not well-typed. In any case, the standard
theorems of preservation and progress are just one way to prove type
safety, which states that a well-typed term cannot be stuck -- a
weaker statement that does not require typechecking intermediate
steps. We are developing a proof of type safety using logical
relations.
